SAT Competition 2020\tnoteref{title}

### 2021-01-12 paper/main.tex
refined table of solvers

\newcommand{\todo}[1]{{\color{purple}Todo: #1}}
\newcommand{\solver}[1]{\texttt{#1}}

@@

\begin{table}
\caption{Main ALL}
\label{tab:mainALL}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
1  & 3926.2 & 264 & {\bf Kissat-sc2020-sat} \\
(1)& 4083.1 & 260 & Kissat-sc2020-default \\
2  & 4179.3 & 253 & {\bf Relaxed\_LCMDCBDL\_newTech} \\
3  & 4266.7 & 248 & {\bf cryptominisat-ccnr-lsids} \\
(3)& 4278.0 & 250 & cryptominisat-ccnr \\
   & 4428.1 & 250 & cadical-alluip-trail \\
   & 4429.6 & 250 & cadical-alluip \\
   & 4436.5 & 245 & Relaxed\_LCMDCBDL \\
   & 4501.2 & 243 & cryptominisat-walksat \\
   & 4554.0 & 243 & cadical-trail \\
   & 4560.0 & 238 & Kissat-sc2020-unsat \\
   & 4607.6 & 246 & CaDiCaL-sc2020 \\
   & 5157.7 & 216 & Undominated-LC-MapleLCMDiscChronoBT-DL \\
   & 5159.6 & 220 & MapleLCMDistChronoBT-DL-f2trc \\
   & 5177.0 & 214 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\   
\end{tabular}
\end{table}

\begin{table}
\caption{Main SAT}
\label{tab:mainSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 2997.4 & 150 & {\bf Relaxed\_LCMDCBDL\_newTech} \\
 2 & 3127.6 & 146 & {\bf Kissat-sc2020-sat} \\
 3 & 3263.0 & 144 & {\bf cryptominisat-ccnr-lsids} \\
(3)& 3317.4 & 145 & cryptominisat-ccnr \\
   & 3355.5 & 143 & Relaxed\_LCMDCBDL \\
   & 3524.7 & 140 & cryptominisat-ccnr-nolimits \\
   & 3622.4 & 138 & cryptominisat-ccnr-lsids-nolimits \\
   & 3703.7 & 140 & cryptominisat-walksat-nolimits \\
   & 3721.2 & 139 & cryptominisat-walksat \\
   & 3830.5 & 134 & Kissat-sc2020-default \\
   & 3908.5 & 135 & cadical-alluip-trail \\
   & 3909.6 & 135 & cadical-alluip \\
   & 4265.6 & 126 & cadical-trail \\
   & 4368.6 & 130 & CaDiCaL-sc2020 \\
   & 4804.9 & 114 & Kissat-sc2020-unsat \\
\end{tabular}
\end{table}

\begin{table}
\caption{Main UNSAT}
\label{tab:mainUNSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
1  & 4315.1 & 124 & {\bf Kissat-sc2020-unsat} \\
(1)& 4335.6 & 126 & Kissat-sc2020-default \\
(1)& 4724.8 & 118 & Kissat-sc2020-sat \\
 2 & 4842.5 & 117 & {\bf cadical-trail} \\
-- & 4846.7 & 116 & CaDiCaL-sc2020 \\
(2)& 4947.8 & 115 & cadical-alluip-trail \\
(2)& 4949.6 & 115 & cadical-alluip \\
 3 & 4991.4 & 110 & {\bf MapleLCMDistChronoBT-f2trc-s} \\
(3)& 5051.4 & 109 & MapleLCMDistChronoBT-f2trc \\
(3)& 5054.3 & 110 & MapleLCMDistChronoBT-DL-f2trc \\
   & 5069.6 & 109 & Maple\_mix \\
   & 5110.0 & 107 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\
   & 5126.9 & 107 & Maple\_simp \\
   & 5128.9 & 107 & MapleLCMDistChronoBT-DL-v3 \\
   & 5142.2 & 106 & Undominated-LC-MapleLCMDiscChronoBT-DL \\
\end{tabular}
\end{table}

\begin{table}
\caption{Planning (ALL)}
\label{tab:planning}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 6406.9 & 80 & {\bf cadical-alluip-trail} \\
(1)& 6409.3 & 80 & cadical-alluip \\
 2 & 6466.9 & 79 & {\bf cryptominisat-ccnr-lsids} \\
(2)& 6471.9 & 79 & cryptominisat-ccnr \\
(2)& 6472.9 & 79 & cryptominisat-walksat \\
 3 & 6596.4 & 75 & {\bf Kissat-sc2020-unsat} \\
   & 6650.1 & 79 & cadical-trail \\
   & 6713.0 & 75 & Maple\_mix \\
   & 6746.5 & 75 & MapleCOMSPS\_LRB\_VSIDS\_2\_\_LRB\_VSIDS\_2\_init \\
   & 6754.3 & 73 & Maple\_simp \\
   & 6773.0 & 73 & MapleCOMSPS\_LRB\_VSIDS\_2\_\_default\_drup \\
   & 6773.9 & 73 & Kissat-sc2020-sat \\
   & 6774.2 & 73 & Kissat-sc2020-default \\
   & 7003.0 & 69 & optsat\_m20 \\
   & 7025.5 & 68 & upGlucose-3.0\_PADC \\
\end{tabular}
\end{table}

@@

\renewcommand{\solver}[1]{\underline{\texttt{#1}}}
\newcommand{\solbert}[1]{\texttt{#1}}

\begin{table}[ht!]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\bf Team & \bf Base Solver & \bf Variant / Name & \bf Award \\
\hline

\multirow{3}{*}{Biere} & \multirow{3}{*}{\solver{Kissat}} &  -- & \firsto, \firstu\\
 &  &  \solbert{sat} & \firsto, \firstu, \seconds\\
 &  &  \solbert{unsat} & \firstu, \thirdp\\
\hline
 Biere, Fleury &  \solbert{Cadical} & \solver{SC2020} & \\
\hline

\multirow{2}{*}{Zhang, Cai}
    & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
% &  & \solbert{Rel. noTimeParam} & \\
 &  & \solbert{Rel. newTech} & \secondo, \firsts\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 &  \multirow{2}{*}{\solbert{CryptoMiniSat-CCAnr}} &  -- & \thirdo, \thirds, \secondp\\
 &  &  \solbert{lsids} & \thirdo, \thirds, \secondp\\
\hline

\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solbert{CryptoMiniSat-WalkSAT} & -- & \\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  \solbert{trail} & \secondu\\
 &  &  \solbert{alluip} & \secondu, \firstp\\
 & \multirow{-3}{*}{\solbert{CaDiCaL}} &  \solver{alluip-trail} & \secondu, \firstp\\
 \cline{2-4}
 & \solbert{MapleLCMDist} & \solbert{alluip-trail} & \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solbert{MapleLCMDistCBT}} & \solver{f2trc} & \thirdu\\
 & & \solbert{f2trc-s} & \thirdu\\
 \cline{2-4}
 & \solbert{MapleLCMDistCBT-DL} & \solbert{f2trc} & \thirdu\\
\hline

\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solver{MapleLCMDistCBT-DL-v3} & -- & \\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
 & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v3}} & \solver{Undominated} & \\
 &  & \solbert{Undom. Top16} & \\
 &  & \solbert{Undom. Top24} & \\
 &  & \solbert{Undom. Top36} & \\
\hline

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{\solver{Ex}\solbert{MapleLCMDistCBT}} & \solbert{padc\_dl} & \\
 &  & \solbert{padc\_dl\_ovau\_lin} & \\
 &  & \solbert{padc\_dl\_ovau\_exp} & \\
 &  & \solbert{psids\_dl} & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & \solbert{MapleLCMDistCBT-DL-v3} & \solver{DurianSat} & \\
\hline

\multirow{2}{*}{Chen}
 & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Maple\_Mix} & \\
 &  & \solver{Maple\_Simp} & \\
\hline

Riveros & \solbert{MapleLCMDistCBT} & \solver{SLIME} & \\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen}
 & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Scavel} & \\
 &  & \solbert{Scavel01} & \\
 &  & \solbert{Scavel02} & \\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & \multirow{2}{*}{\solver{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & \\
 &  & \solbert{init} & \\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v2.2}} & \solver{exp}\solbert{-V-LGB} & \\
 &  & \solbert{exp-V-L} & \\
 &  & \solbert{exp-L} & \\
 &  & \solbert{exp-V} & \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{\solver{MapleCM}} & \solver{+dist} & \\
 &  & \solbert{+dist+sattime2s+-} & \\
 &  & \solbert{+dist+simp2--} & \\
 &  & \solbert{used+dist} & \\
\hline

Kaiser, Hartung & \solbert{MapleLCMDist} & \solver{PauSat} & \\
\hline

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solver{ParaFROST}} & -- & \\
 &  & \solbert{CBT} & \\
\hline
\end{tabular}
\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: Column~2 highlights the recent genealogy of submissions and Column~3 displays configuration names as well as names of forks. We partially \solver{underlined} submission names. Awards in the Main- (M), Planning- (P), Sat- (s), and Unsat- (u) Tracks are indicated by a string TX with $T \in \{M, P, s, u\}$ and $X \in \{1,2,3\}$. }
\label{tab:solvers-main}
\end{table}

\renewcommand{\solver}[1]{\texttt{#1}} % sorry ;)

@@

The Virtual Best Solver (VBS) is a fictitious solver consisting 
of all the solvers that actually participated in the competition (or a specific track)
and an oracle which, when given an input instance,
invokes to run the actual solver which performed the best on that instance.
In this way, the performance of the VBS highlights a certain upper bound 
on performance achievable in principle by the technology 
of the participating solvers (cf. the figures in Section~\ref{sec:results}).

@@

\begin{table}
\caption{VBS metrics for the results of the Main track, all instances. 
The total number of solved problems was 317. 
There were 60 (non-disqualified) solvers (and their configurations).
Each table shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainALL}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
46 & 11.5 & Kissat-sc2020-unsat \\
37 & \phantom{0}9.2 & Kissat-sc2020-sat \\
22 & \phantom{0}5.5 & Kissat-sc2020-default \\
14 & \phantom{0}3.5 & Maple\_CM+dist+sattime2s+- \\
13 & \phantom{0}3.2 & cryptominisat-ccnr-lsids \\
13 & \phantom{0}3.2 & Maple-LCM-Dist-alluip-trail \\
12 & \phantom{0}3.0 & Relaxed\_LCMDCBDL \\
11 & \phantom{0}2.8 & upGlucose-3.0\_PADC \\
10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
\phantom{0}9 & \phantom{0}2.2 & Maple\_CMused+dist \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
129.8 & 32.4 & Kissat-sc2020-sat \\
120.1 & 30.0 & Kissat-sc2020-default \\
113.6 & 28.4 & Kissat-sc2020-unsat \\
\phantom{0}91.0 & 22.7 & cryptominisat-ccnr-lsids \\
\phantom{0}87.0 & 21.7 & cryptominisat-ccnr \\
\phantom{0}82.0 & 20.5 & cadical-alluip-trail \\
\phantom{0}81.9 & 20.5 & cadical-alluip \\
\phantom{0}81.8 & 20.5 & CaDiCaL-sc2020 \\
\phantom{0}81.0 & 20.2 & Relaxed\_LCMDCBDL\_newTech \\
\phantom{0}80.5 & 20.1 & Relaxed\_LCMDCBDL \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
11.7 & 2.9 & Kissat-sc2020-default \\
10.8 & 2.7 & Kissat-sc2020-unsat \\
10.4 & 2.6 & Relaxed\_LCMDCBDL\_newTech \\
\phantom{0}9.9 & 2.5 & Kissat-sc2020-sat \\
\phantom{0}9.8 & 2.4 & cadical-alluip \\
\phantom{0}9.8 & 2.4 & cadical-alluip-trail \\
\phantom{0}9.4 & 2.3 & Relaxed\_LCMDCBDL \\
\phantom{0}9.4 & 2.3 & CaDiCaL-sc2020 \\
\phantom{0}8.7 & 2.2 & cadical-trail \\
\phantom{0}8.3 & 2.1 & cryptominisat-walksat \\
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{VBS metrics for the results of the Main track, SAT instances. 
The total number of solved problems was 183. 
There were 60 (non-disqualified) participating solvers.
Each table always shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainSAT}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
27 & 14.8 & Kissat-sc2020-sat \\
14 & \phantom{0}7.7 & Maple\_CM+dist+sattime2s+- \\
12 & \phantom{0}6.6 & Kissat-sc2020-default \\
10 & \phantom{0}5.5 & Relaxed\_LCMDCBDL \\
\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
\phantom{0}8 & \phantom{0}4.4 & Kissat-sc2020-unsat \\
\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids-nolimits \\
\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids \\
\phantom{0}6 & \phantom{0}3.3 & cadical-trail \\
\phantom{0}6 & \phantom{0}3.3 & cryptominisat-ccnr-nolimits \\

\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
68.5 & 37.4 & Kissat-sc2020-sat \\
46.3 & 25.3 & Kissat-sc2020-default \\
44.1 & 24.1 & cryptominisat-ccnr-lsids \\
42.2 & 23.0 & Relaxed\_LCMDCBDL\_newTech \\
41.8 & 22.9 & cryptominisat-ccnr-lsids-nolimits \\
40.9 & 22.3 & cryptominisat-ccnr \\
40.6 & 22.2 & Relaxed\_LCMDCBDL \\
39.4 & 21.5 & cryptominisat-ccnr-nolimits \\
35.2 & 19.2 & cryptominisat-walksat-nolimits \\
32.8 & 17.9 & cryptominisat-walksat \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
8.0 & 4.4 & Relaxed\_LCMDCBDL\_newTech \\
7.0 & 3.8 & Relaxed\_LCMDCBDL \\
6.5 & 3.6 & cryptominisat-walksat-nolimits \\
5.8 & 3.2 & cryptominisat-walksat \\
5.6 & 3.0 & Kissat-sc2020-sat \\
5.4 & 3.0 & cryptominisat-ccnr-lsids \\
5.4 & 3.0 & Kissat-sc2020-default \\
5.4 & 2.9 & cryptominisat-ccnr \\
5.2 & 2.8 & cadical-alluip \\
5.2 & 2.8 & cadical-alluip-trail \\
\end{tabular}
\end{center}
\end{table}

>>>>

\newcommand{\todo}[1]{{\color{purple}Todo: #1}}
\newcommand{\solver}[1]{\texttt{#1}}
\newcommand{\solbert}[1]{\underline{\solver{#1}}}

@@

\begin{table}
\caption{Main ALL}
\label{tab:mainALL}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
1     & 3926.2 & 264 & {\bf Kissat-sat} \\
(1)   & 4083.1 & 260 & Kissat \\
2     & 4179.3 & 253 & {\bf Relaxed\_newTech} \\
3     & 4266.7 & 248 & {\bf CMS-ccnr-lsids} \\
(3)   & 4278.0 & 250 & CMS-ccnr \\
      & 4428.1 & 250 & CaDiCaL-alluip-trail \\
      & 4429.6 & 250 & CaDiCaL-alluip \\
      & 4436.5 & 245 & Relaxed \\
      & 4501.2 & 243 & CMS-walksat \\
      & 4554.0 & 243 & CaDiCaL-trail \\
      & 4560.0 & 238 & Kissat-unsat \\
      & 4607.6 & 246 & CaDiCaL-sc2020 \\
      & 5157.7 & 216 & Undominated \\
      & 5159.6 & 220 & f2trc-DL \\
      & 5177.0 & 214 & PADC\_DL \\   
\end{tabular}
\end{table}

\begin{table}
\caption{Main SAT}
\label{tab:mainSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1    & 2997.4 & 150 & {\bf Relaxed\_newTech} \\
 2    & 3127.6 & 146 & {\bf Kissat-sat} \\
 3    & 3263.0 & 144 & {\bf CMS-ccnr-lsids} \\
(3)   & 3317.4 & 145 & CMS-ccnr \\
      & 3355.5 & 143 & Relaxed \\
      & 3721.2 & 139 & CMS-walksat \\
      & 3830.5 & 134 & Kissat \\
      & 3908.5 & 135 & CaDiCaL-alluip-trail \\
      & 3909.6 & 135 & CaDiCaL-alluip \\
      & 4265.6 & 126 & CaDiCaL-trail \\
      & 4368.6 & 130 & CaDiCaL-sc2020 \\
      & 4804.9 & 114 & Kissat-unsat \\
      & 5173.2 & 110 & Undominated \\
      & 5206.0 & 110 & abcdsat\_n20 \\
      & 5244.1 & 107 & PADC\_DL \\   
\end{tabular}
\end{table}

\begin{table}
\caption{Main UNSAT}
\label{tab:mainUNSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline   
1     & 4315.1 & 124 & {\bf Kissat-unsat} \\
(1)   & 4335.6 & 126 & Kissat \\
(1)   & 4724.8 & 118 & Kissat-sat \\
 2    & 4842.5 & 117 & {\bf CaDiCaL-trail} \\
--    & 4846.7 & 116 & CaDiCaL-sc2020 \\
(2)   & 4947.8 & 115 & CaDiCaL-alluip-trail \\
(2)   & 4949.6 & 115 & CaDiCaL-alluip \\
 3    & 4991.4 & 110 & {\bf f2trc-s} \\
(3)   & 5051.4 & 109 & f2trc \\
(3)   & 5054.3 & 110 & f2trc-DL \\
      & 5069.6 & 109 & Maple\_Mix \\
      & 5110.0 & 107 & PADC\_DL \\
      & 5126.9 & 107 & Maple\_Simp \\
      & 5128.9 & 107 & MapleCBT-DL-v3 \\
      & 5142.2 & 106 & Undominated \\
\end{tabular}
\end{table}

\begin{table}
\caption{Planning (ALL)}
\label{tab:planning}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline   
 1    & 6406.9 & 80 & {\bf CaDiCaL-alluip-trail} \\
(1)   & 6409.3 & 80 & CaDiCaL-alluip \\
 2    & 6466.9 & 79 & {\bf CMS-ccnr-lsids} \\
(2)   & 6471.9 & 79 & CMS-ccnr \\
(2)   & 6472.9 & 79 & CMS-walksat \\
 3    & 6596.4 & 75 & {\bf Kissat-unsat} \\
      & 6650.1 & 79 & CaDiCaL-trail \\
      & 6713.0 & 75 & Maple\_Mix \\
      & 6746.5 & 75 & MapleCOMSPS\_init \\
      & 6754.3 & 73 & Maple\_Simp \\
      & 6773.0 & 73 & MapleCOMSPS\_drup \\
      & 6773.9 & 73 & Kissat-sat \\
      & 6774.2 & 73 & Kissat \\
      & 7003.0 & 69 & optsat\_m20 \\
      & 7025.5 & 68 & upGlucose3.0\_PADC \\
\end{tabular}
\end{table}

@@

\begin{table}[ht!]
\setlength\tabcolsep{4.5pt}
\smaller
\centering
\begin{tabular}{lllcccc}
\bf Team & \bf Base Solver & \bf Variant / Name & \bf M & \bf U & \bf S & \bf P \\
\hline
\arrayrulecolor{lightgray}

\multirow{3}{*}{Biere} & \multirow{3}{*}{\solbert{Kissat}} &  -- & 1 & 1 & -- & --\\
 &  &  \solver{sat} & 1 & 1 & 2 & --\\
 &  &  \solver{unsat} & -- & 1 & -- & 3\\
\hline
 Biere, Fleury &  \solver{Cadical} & \solbert{SC2020} & -- & -- & -- & --\\
\hline

\multirow{2}{*}{Zhang, Cai}
    & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Relaxed} & -- & -- & -- & --\\
% &  & \solver{Rel. noTimeParam} & \\
 &  & \solver{Rel. newTech} & 2 & -- & 1 & --\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 &  \multirow{2}{*}{\solver{CryptoMiniSat-CCAnr}} &  -- & 3 & -- & 3 & 2\\
 &  &  \solver{lsids} & 3 & -- & 3 & 2\\
\hline

\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solver{CryptoMiniSat-WalkSAT} & -- & -- & -- & -- & --\\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  \solver{trail} & -- & 2 & -- & --\\
 &  &  \solver{alluip} & -- & 2 & -- & 1\\
 & \multirow{-3}{*}{\solver{CaDiCaL}} &  \solbert{alluip-trail} & -- & 2 & -- & 1\\
 \cline{2-7}
 & \solver{MapleLCMDist} & \solver{alluip-trail} & -- & -- & -- & -- \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solver{MapleLCMDistCBT}} & \solbert{f2trc} & -- & 3 & -- & --\\
 & & \solver{f2trc-s} & -- & 3 & -- & --\\
 \cline{2-7}
 & \solver{MapleLCMDistCBT-DL} & \solver{f2trc} & -- & 3 & -- & --\\
\hline

\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solbert{MapleLCMDistCBT-DL-v3} & -- & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
 & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v3}} & \solbert{Undominated} & -- & -- & -- & -- \\
 &  & \solver{Undom. Top16} & -- & -- & -- & -- \\
 &  & \solver{Undom. Top24} & -- & -- & -- & -- \\
 &  & \solver{Undom. Top36} & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{\solbert{Ex}\solver{MapleLCMDistCBT}} & \solver{padc\_dl} & -- & -- & -- & -- \\
 &  & \solver{padc\_dl\_ovau\_lin} & -- & -- & -- & -- \\
 &  & \solver{padc\_dl\_ovau\_exp} & -- & -- & -- & -- \\
 &  & \solver{psids\_dl} & -- & -- & -- & -- \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & \solver{MapleLCMDistCBT-DL-v3} & \solbert{DurianSat} & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{Chen}
 & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Maple\_Mix} & -- & -- & -- & -- \\
 &  & \solbert{Maple\_Simp} & -- & -- & -- & -- \\
\hline

Riveros & \solver{MapleLCMDistCBT} & \solbert{SLIME} & -- & -- & -- & -- \\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen}
 & \multirow{3}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Scavel} & -- & -- & -- & -- \\
 &  & \solver{Scavel01} & -- & -- & -- & -- \\
 &  & \solver{Scavel02} & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & \multirow{2}{*}{\solbert{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & -- & -- & -- & -- \\
 &  & \solver{init} & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v2.2}} & \solbert{exp}\solver{-V-LGB} & -- & -- & -- & -- \\
 &  & \solver{exp-V-L} & -- & -- & -- & -- \\
 &  & \solver{exp-L} & -- & -- & -- & -- \\
 &  & \solver{exp-V} & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{\solbert{MapleCM}} & \solbert{+dist} & -- & -- & -- & -- \\
 &  & \solver{+dist+sattime2s+-} & -- & -- & -- & -- \\
 &  & \solver{+dist+simp2--} & -- & -- & -- & -- \\
 &  & \solver{used+dist} & -- & -- & -- & -- \\
\hline

Kaiser, Hartung & \solver{MapleLCMDist} & \solbert{PauSat} & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- \\
 &  & \solver{CBT} & -- & -- & -- & -- 
\end{tabular}
\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: Column~2 highlights the recent genealogy of submissions and Column~3 displays configuration names as well as names of forks. We partially \solbert{underlined} submission names. Awards in the Main- (M), Planning- (P), Sat- (s), and Unsat- (u) Tracks are indicated by a string TX with $T \in \{M, P, s, u\}$ and $X \in \{1,2,3\}$. }
\label{tab:solvers-main}
\end{table}

@@

The Virtual Best Solver (VBS) is a fictitious solver consisting 
of all the solvers that actually participated in the competition (or a specific track)
and an oracle which, when given an input instance,
invokes to run the actual solver which performed the best on that instance.
In this way, the performance of the VBS highlights a certain upper bound 
on performance achievable in principle by the technology 
of the participating solvers (cf.~the figures in Section~\ref{sec:results}).

@@

\begin{table}
\caption{VBS metrics for the results of the Main track, all instances. 
The total number of solved problems was 316. 
There were 54 (non-disqualified) solvers (and their configurations).
Each table shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainALL}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
46 & 11.5 & Kissat-unsat \\
37 & \phantom{0}9.2 & Kissat-sat \\
24 & \phantom{0}6.0 & Kissat \\
18 & \phantom{0}4.5 & CMS-ccnr-lsids \\
14 & \phantom{0}3.5 & MapleCM+dist+sat2s \\
13 & \phantom{0}3.2 & Maple-alluip-trail \\
12 & \phantom{0}3.0 & Relaxed \\
11 & \phantom{0}2.8 & upGlucose3.0\_PADC \\
10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
\phantom{0}9 & \phantom{0}2.2 & CMS-ccnr \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
130.3 & 32.6 & Kissat-sat \\
120.7 & 30.2 & Kissat \\
114.0 & 28.5 & Kissat-unsat \\
\phantom{0}91.5 & 22.9 & CMS-ccnr-lsids \\
\phantom{0}87.8 & 22.0 & CMS-ccnr \\
\phantom{0}82.3 & 20.6 & CaDiCaL-alluip-trail \\
\phantom{0}82.2 & 20.5 & CaDiCaL-alluip \\
\phantom{0}81.9 & 20.5 & CaDiCaL-sc2020 \\
\phantom{0}81.4 & 20.4 & Relaxed\_newTech \\
\phantom{0}80.8 & 20.2 & Relaxed \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
12.4 & 3.1 & Kissat \\
11.4 & 2.9 & Kissat-unsat \\
11.4 & 2.8 & Relaxed\_newTech \\
10.7 & 2.7 & Kissat-sat \\
10.3 & 2.6 & CaDiCaL-alluip-trail \\
10.3 & 2.6 & CaDiCaL-alluip \\
10.0 & 2.5 & Relaxed \\
\phantom{0}9.9 & 2.5 & CaDiCaL-sc2020 \\
\phantom{0}9.7 & 2.4 & CMS-walksat \\
\phantom{0}9.2 & 2.3 & CaDiCaL-trail \\
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{VBS metrics for the results of the Main track, SAT instances. 
The total number of solved problems was 182. 
There were 54 (non-disqualified) participating solvers.
Each table always shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainSAT}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
27 & 14.8 & Kissat-sat \\
14 & \phantom{0}7.7 & MapleCM+dist+sat2s \\
14 & \phantom{0}7.7 & Kissat \\
12 & \phantom{0}6.6 & CMS-ccnr-lsids \\
10 & \phantom{0}5.5 & Relaxed \\
\phantom{0}8 & \phantom{0}4.4 & CMS-ccnr \\
\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
\phantom{0}8 & \phantom{0}4.4 & Kissat-unsat \\
\phantom{0}6 & \phantom{0}3.3 & CaDiCaL-trail \\
\phantom{0}5 & \phantom{0}2.7 & MapleCOMSPS\_drup \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
69.0 & 37.9 & Kissat-sat \\
46.9 & 25.7 & Kissat \\
44.6 & 24.5 & CMS-ccnr-lsids \\
42.6 & 23.4 & Relaxed\_newTech \\
41.7 & 22.9 & CMS-ccnr \\
41.0 & 22.5 & Relaxed \\
33.1 & 18.2 & CMS-walksat \\
32.9 & 18.1 & CaDiCaL-alluip-trail \\
32.8 & 18.0 & CaDiCaL-alluip \\
31.8 & 17.5 & CaDiCaL-sc2020 \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
9.0 & 4.9 & Relaxed\_newTech \\
7.7 & 4.2 & Relaxed \\
7.3 & 4.0 & CMS-walksat \\
6.4 & 3.5 & Kissat-sat \\
6.2 & 3.4 & CMS-ccnr-lsids \\
6.2 & 3.4 & Kissat \\
6.2 & 3.4 & CMS-ccnr \\
5.7 & 3.2 & CaDiCaL-alluip-trail \\
5.7 & 3.2 & CaDiCaL-alluip \\
5.7 & 3.1 & CaDiCaL-sc2020 \\
\end{tabular}
\end{center}
\end{table}
